---
title: "Assignment 2 Task 3"
author: "Jessica Jagdeo"
date: "2/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)
```


This project displays an interactive agricultural land use/land cover and watershed distribution map of the Hawaiian Islands. This map can be utilized to determine the composition of agricultural land use and land cover within a specific watershed. This can be useful for hydrological modeling projects in predominantly agricultural regions within Hawaiian watersheds. 


#### 1. Load necessary packages.
```{r}

library(tidyverse)
library(janitor)
library(kableExtra)
library(naniar)
library(skimr)
library(sf)
library(tmap)
library(paletteer)
library(lubridate)
library(here)

```

#### 2. Read in the data: watersheds and land use/land cover for the Hawaiian Islands
```{r}

watershed <- read_sf(dsn = here(".", "Watersheds"),
                 layer = "Watersheds") %>% 
              st_transform(crs = 4326) # Set the coordinate reference system 

lulc <- read_sf(dsn = here(".", "Land_Use_Land_Cover_LULC"),
                layer = "Land_Use_Land_Cover_LULC") %>% 
              st_transform(crs = 4326) %>% 
  filter(landcover == "Cropland and Pasture" |
           landcover == "Shrub and Brush Rangeland" |
           landcover == "Orchards, Groves, Vineyards, Nurseries and Ornamental Horticultural Areas" |
           landcover == "Herbaceous Rangeland" |
           landcover == "Mixed Rangeland" |
           landcover == "Other Agricultural Land") # For the purposes of this map, interested in displaying rangeland and agricultural areas, so filtering out other land covers

```

#### 3. Create an interactive map of the watersheds and land use/land cover for the Hawaiian Islands

```{r, out.width = "100%"}

hawaii_tmap <- tm_basemap("Esri.WorldImagery") + # Put in a basemap
  tm_shape(watershed) +
  tm_borders("lightblue", lwd = .5) +
  tm_shape(lulc) +
  tm_fill("landcover", 
          title = "Land Cover", 
          palette = c("orange", "purple", "blue", "yellow"), 
          alpha = 0.5) +
  tm_layout("Agricultural Land Use/Land Cover for Watersheds of the Hawaiian Islands") +
  tm_view(view.legend.position = c("left", "bottom"))

tmap_mode("view") # Sets it to interactive view

hawaii_tmap

```


**Figure 1. Agricultural land use/land cover and watershed distribution of the Hawaiian Islands.** Data source: Hawaiian Statewide GIS Program. 